Weighted Model Counting with Conditional Weights

### 2020-08-16 paper/paper.tex
A bit more experimental data
New data

In this section, we describe an experimental study comparing the five WMC
encodings for Bayesian networks when run with ADDMC. The experiments were run on
Intel Xeon Gold 6138 processor with an \SI{8}{\giga\byte} memory limit.

@@

\paragraph{Data.} For experimental data, we use the Bayesian networks available
with Ace and
Cachet\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}, most of
which happen to be binary. We classify them into the following seven categories:
\begin{itemize*}
\item DQMR and
\item Grid networks as described by \citet{DBLP:conf/aaai/SangBK05},
\item Friends and Smokers,
\item Mastermind, and
\item Random Blocks from the work of \citet{DBLP:journals/ijar/ChaviraDJ06},
\item remaining binary Bayesian networks that include Plan Recognition
  \cite{DBLP:conf/aaai/SangBK05}, Students and Professors
  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
\item non-binary classic Bayesian networks (\texttt{alarm}, \texttt{diabetes},
  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
  \texttt{pathfinder}, \texttt{pigs}, \texttt{water}).
\end{itemize*}

@@

% TODO: (needed to follow formatting requirements)
% 1. Remove the \input command.
% 2. R should compile the tex files to be standalone.
% 3. Edit the tex files to replace RGB colours with CMYK.
% 4. Compile the tex files to PDFs.
% 5. Include the PDFs (look up how to do that in the formatting guidelines).

\begin{table}
  \centering
  \caption{The numbers of instances solved by ADDMC with each encoding
    (uniquely, faster than with others, and in total) under the described time
    and memory constraints (out of 1216 instances)}%
  \begin{tabular}{lrrr}
    \toprule
    Encoding & Unique & Fastest & Total \\
    \midrule
    \texttt{cd05} & 2 & 3 & 372 \\
    \texttt{cd06} & 0 & 1 & 351 \\
    \texttt{cw} & 228 & 871 & 901 \\
    \texttt{d02} & 41 & 99 & 726 \\
    \texttt{sbk05} & 6 & 36 & 687 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

% TODO: write. then run through a grammar checker.
\paragraph{Observations.}
\begin{itemize}
\item The order of the encodings from best to worst is exactly the opposite of
  that in the previous literature.
\item Our encoding is particularly promising on instances of Grid networks.
  They are set up so that the entire Bayesian network is relevant to the
  query.
\item However, \texttt{cw} struggles with instances from Mastermind and
  Random Blocks domains (but so does \texttt{sbk05}). We conjecture that this
  is so either because the particular structure of these problems confuse the
  heuristics used by ADDMC or because these instances allow for significant
  simplifications that are exploited by \texttt{d02} but not \texttt{cw}.
\item An observation from the cumulative plot: \texttt{cw} solves the same
  number of instances in \SI{6.374}{\second} as \texttt{d02} does in
  \SI{1000}{\second}.
\end{itemize}

>>>>

In this section, we describe an experimental study comparing the five WMC
encodings for Bayesian networks when run with ADDMC. The experiments were run on
Intel Xeon Gold 6138 and Intel Xeon E5-2630 processors\footnote{Each instance is
run on the same processor for all encodings.} with an \SI{8}{\gibi\byte} memory
limit.

@@

\paragraph{Data.} For experimental data, we use the Bayesian networks available
with Ace and
Cachet\footnote{\url{https://www.cs.rochester.edu/u/kautz/Cachet/}}, most of
which happen to be binary. We classify them into the following seven categories:
\begin{itemize*}
\item DQMR and
\item Grid networks as described by \citet{DBLP:conf/aaai/SangBK05},
\item Mastermind, and
\item Random Blocks from the work of \citet{DBLP:journals/ijar/ChaviraDJ06},
\item remaining binary Bayesian networks that include Plan Recognition
  \cite{DBLP:conf/aaai/SangBK05}, Friends and Smokers, Students and Professors
  \cite{DBLP:journals/ijar/ChaviraDJ06}, and \texttt{tcc4f}, and
\item non-binary classic Bayesian networks (\texttt{alarm}, \texttt{diabetes},
  \texttt{hailfinder}, \texttt{mildew}, \texttt{munin1}--\texttt{4},
  \texttt{pathfinder}, \texttt{pigs}, \texttt{water}).
\end{itemize*}
% TODO: make sure to talk about the table (and mention that cd06 has its niche)

@@

% TODO: (needed to follow formatting requirements)
% 1. Remove the \input command.
% 2. R should compile the tex files to be standalone.
% 3. Edit the tex files to replace RGB colours with CMYK.
% 4. Compile the tex files to PDFs.
% 5. Include the PDFs (look up how to do that in the formatting guidelines).
% 6. make sure that there are no duplicates in the bib files (look at LaTex output)

% TODO: check if the total checks out

\begin{table}
  \centering
  \caption{The numbers of instances (out of 1451) solved by ADDMC with each
    encoding (uniquely, faster than with others, and in total) under the
    described time and memory constraints}%
  \begin{tabular}{lrrr}
    \toprule
    Encoding & Unique & Fastest & Total \\
    \midrule
    \texttt{cd05} & 2 & 76 & 380 \\
    \texttt{cd06} & 0 & 214 & 363 \\
    \texttt{cw} & 234 & 633 & 965 \\
    \texttt{d02} & 40 & 58 & 782 \\
    \texttt{sbk05} & 12 & 16 & 750 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

% TODO: write. then run through a grammar checker.
\paragraph{Observations.}
\begin{itemize}
\item The order of the encodings from best to worst is exactly the opposite of
  that in the previous literature.
\item Our encoding is particularly promising on instances of Grid networks.
  They are set up so that the entire Bayesian network is relevant to the
  query.
\item However, \texttt{cw} struggles with instances from Mastermind and
  Random Blocks domains (but so does \texttt{sbk05}). We conjecture that this
  is so either because the particular structure of these problems confuse the
  heuristics used by ADDMC or because these instances allow for significant
  simplifications that are exploited by \texttt{d02} but not \texttt{cw}.
\item An observation from the cumulative plot: \texttt{cw} solves the same
  number of instances in \SI{8.144}{\second} as \texttt{d02} does in
  \SI{1000}{\second}.
\end{itemize}
